decompr: GVC decomposition in R

### 2015-01-27 draft.Rnw
recompile

\documentclass{article}

@@

\begin{document}
\SweaveOpts{concordance=TRUE}
\maketitle

@@

<<load-data >>=
# load the data
data(leather)
# list the objects in the data set
ls()
@

@@

\subsection{Implentation}
The first step is to load the data and create the elements, there are all stored in a list (of class **decompr**).

@@

In addition, a wrapper function called **decomp** is provided which performs both steps at once.
Though it is recomended that the atomic functions be used for large data sets.

>>>>

\documentclass[a4paper,twoside]{article}

@@

\begin{document}
\maketitle

@@

<<load-data >>=
# load the data
data(leather)

# list the objects in the data set
ls()
@

@@

\subsection{Implentation}
The first step is to load the data and create the elements, there are all stored in a list (of class \textbf{decompr}).

@@

In addition, a wrapper function called \textbf{decomp} is provided which performs both steps at once.
Though it is recomended that the atomic functions be used for large data sets.

### 2015-01-27 draft.tex
recompile

\documentclass{article}

@@

\title{decompr: GVC decomposition in R}
\author{Bastiaan Quast and Victor Kummritz}

\usepackage{Sweave}
\begin{document}
\input{draft-concordance}
\maketitle

@@

\begin{Schunk}
\begin{Sinput}
> # load the package
> library(decompr)
\end{Sinput}
\end{Schunk}

\begin{Schunk}
\begin{Sinput}
> # load the data
> data(leather)
> # list the objects in the data set
> ls()
\end{Sinput}
\begin{Soutput}
[1] "countries"  "final"      "industries" "inter"      "out"       
\end{Soutput}
\end{Schunk}

@@

\subsection{Implentation}
The first step is to load the data and create the elements, there are all stored in a list (of class **decompr**).

\begin{Schunk}
\begin{Sinput}
> decompr_object <- load_tables_vectors( x = inter,
+                                        y = final,
+                                        k = countries,
+                                        i = industries,
+                                        o = out         )
\end{Sinput}
\end{Schunk}

We can now decompose the elements using the Leontief decomposition.
\begin{Schunk}
\begin{Sinput}
> lt <- leontief( decompr_object )
\end{Sinput}
\end{Schunk}

In addition, a wrapper function called **decomp** is provided which performs both steps at once.
Though it is recomended that the atomic functions be used for large data sets.

\begin{Schunk}
\begin{Sinput}
> lt2 <- decomp( x = inter,
+                y = final,
+                k = countries,
+                i = industries,
+                o = out,
+                method = "leontief" )
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> lt
\end{Sinput}
\begin{Soutput}
                              Argentina.Agriculture
Argentina.Agriculture                   28.52278143
Argentina.Textile.and.Leather            1.06206936
Argentina.Transport.Equipment            0.21043693
Turkey.Agriculture                       0.71952151
Turkey.Textile.and.Leather               0.41201175
Turkey.Transport.Equipment               0.03482652
Germany.Agriculture                      0.92530356
Germany.Textile.and.Leather              0.64666560
Germany.Transport.Equipment              0.66638333
                              Argentina.Textile.and.Leather
Argentina.Agriculture                            2.79395126
Argentina.Textile.and.Leather                   19.12053186
Argentina.Transport.Equipment                    0.14228369
Turkey.Agriculture                               1.34237213
Turkey.Textile.and.Leather                       1.38523849
Turkey.Transport.Equipment                       0.08553139
Germany.Agriculture                              2.25142713
Germany.Textile.and.Leather                      0.72785683
Germany.Transport.Equipment                      0.65080723
                              Argentina.Transport.Equipment Turkey.Agriculture
Argentina.Agriculture                            0.35606694         1.81066955
Argentina.Textile.and.Leather                    0.41813924         0.48370042
Argentina.Transport.Equipment                    1.06369578         0.03329456
Turkey.Agriculture                               0.11504126        34.92704803
Turkey.Textile.and.Leather                       0.11764036         2.69291816
Turkey.Transport.Equipment                       0.02667530         0.81210167
Germany.Agriculture                              0.16222512         2.31122022
Germany.Textile.and.Leather                      0.08244379         1.53837777
Germany.Transport.Equipment                      0.25807221         1.29066963
                              Turkey.Textile.and.Leather
Argentina.Agriculture                          3.1173841
Argentina.Textile.and.Leather                  1.8329024
Argentina.Transport.Equipment                  0.0790545
Turkey.Agriculture                             6.9994970
Turkey.Textile.and.Leather                    40.1671410
Turkey.Transport.Equipment                     0.9075189
Germany.Agriculture                            2.0595825
Germany.Textile.and.Leather                    2.5488967
Germany.Transport.Equipment                    1.4880228
                              Turkey.Transport.Equipment Germany.Agriculture
Argentina.Agriculture                         0.35901126           1.2364172
Argentina.Textile.and.Leather                 0.43058635           0.5937041
Argentina.Transport.Equipment                 0.04024626           0.0231846
Turkey.Agriculture                            1.47711579           2.5543089
Turkey.Textile.and.Leather                    1.31799873           1.1093993
Turkey.Transport.Equipment                    3.16041392           0.1151191
Germany.Agriculture                           0.51211484          29.8763359
Germany.Textile.and.Leather                   0.63316614           1.4593583
Germany.Transport.Equipment                   0.56934671           1.7321726
                              Germany.Textile.and.Leather
Argentina.Agriculture                          1.30283802
Argentina.Textile.and.Leather                  1.15375958
Argentina.Transport.Equipment                  0.07482343
Turkey.Agriculture                             1.52213499
Turkey.Textile.and.Leather                     1.15207241
Turkey.Transport.Equipment                     0.07448266
Germany.Agriculture                            5.24719728
Germany.Textile.and.Leather                   18.95868110
Germany.Transport.Equipment                    1.51401054
                              Germany.Transport.Equipment
Argentina.Agriculture                           4.1208736
Argentina.Textile.and.Leather                   4.7490351
Argentina.Transport.Equipment                   0.1932621
Turkey.Agriculture                              6.1806254
Turkey.Textile.and.Leather                      9.5069032
Turkey.Transport.Equipment                      0.6464733
Germany.Agriculture                             9.6006931
Germany.Textile.and.Leather                     8.1583150
Germany.Transport.Equipment                    34.7438192
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> w <- wwz(decompr_object)
\end{Sinput}
\end{Schunk}

>>>>

\documentclass[a4paper,twoside]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

@@

\title{decompr: GVC decomposition in R}
\author{Bastiaan Quast and Victor Kummritz}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\maketitle

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{# load the package}
\hlkwd{library}\hlstd{(decompr)}
\end{alltt}
\end{kframe}
\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{# load the data}
\hlkwd{data}\hlstd{(leather)}

\hlcom{# list the objects in the data set}
\hlkwd{ls}\hlstd{()}
\end{alltt}
\begin{verbatim}
## [1] "countries"  "final"      "industries" "inter"      "out"
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\subsection{Implentation}
The first step is to load the data and create the elements, there are all stored in a list (of class \textbf{decompr}).

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{decompr_object} \hlkwb{<-} \hlkwd{load_tables_vectors}\hlstd{(} \hlkwc{x} \hlstd{= inter,}
                                       \hlkwc{y} \hlstd{= final,}
                                       \hlkwc{k} \hlstd{= countries,}
                                       \hlkwc{i} \hlstd{= industries,}
                                       \hlkwc{o} \hlstd{= out        )}
\end{alltt}
\end{kframe}
\end{knitrout}

We can now decompose the elements using the Leontief decomposition.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{lt} \hlkwb{<-} \hlkwd{leontief}\hlstd{( decompr_object )}
\end{alltt}
\end{kframe}
\end{knitrout}

In addition, a wrapper function called \textbf{decomp} is provided which performs both steps at once.
Though it is recomended that the atomic functions be used for large data sets.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{lt2} \hlkwb{<-} \hlkwd{decomp}\hlstd{(} \hlkwc{x} \hlstd{= inter,}
               \hlkwc{y} \hlstd{= final,}
               \hlkwc{k} \hlstd{= countries,}
               \hlkwc{i} \hlstd{= industries,}
               \hlkwc{o} \hlstd{= out,}
               \hlkwc{method} \hlstd{=} \hlstr{"leontief"} \hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{lt}
\end{alltt}
\begin{verbatim}
##                               Argentina.Agriculture
## Argentina.Agriculture                   28.52278143
## Argentina.Textile.and.Leather            1.06206936
## Argentina.Transport.Equipment            0.21043693
## Turkey.Agriculture                       0.71952151
## Turkey.Textile.and.Leather               0.41201175
## Turkey.Transport.Equipment               0.03482652
## Germany.Agriculture                      0.92530356
## Germany.Textile.and.Leather              0.64666560
## Germany.Transport.Equipment              0.66638333
##                               Argentina.Textile.and.Leather
## Argentina.Agriculture                            2.79395126
## Argentina.Textile.and.Leather                   19.12053186
## Argentina.Transport.Equipment                    0.14228369
## Turkey.Agriculture                               1.34237213
## Turkey.Textile.and.Leather                       1.38523849
## Turkey.Transport.Equipment                       0.08553139
## Germany.Agriculture                              2.25142713
## Germany.Textile.and.Leather                      0.72785683
## Germany.Transport.Equipment                      0.65080723
##                               Argentina.Transport.Equipment
## Argentina.Agriculture                            0.35606694
## Argentina.Textile.and.Leather                    0.41813924
## Argentina.Transport.Equipment                    1.06369578
## Turkey.Agriculture                               0.11504126
## Turkey.Textile.and.Leather                       0.11764036
## Turkey.Transport.Equipment                       0.02667530
## Germany.Agriculture                              0.16222512
## Germany.Textile.and.Leather                      0.08244379
## Germany.Transport.Equipment                      0.25807221
##                               Turkey.Agriculture
## Argentina.Agriculture                 1.81066955
## Argentina.Textile.and.Leather         0.48370042
## Argentina.Transport.Equipment         0.03329456
## Turkey.Agriculture                   34.92704803
## Turkey.Textile.and.Leather            2.69291816
## Turkey.Transport.Equipment            0.81210167
## Germany.Agriculture                   2.31122022
## Germany.Textile.and.Leather           1.53837777
## Germany.Transport.Equipment           1.29066963
##                               Turkey.Textile.and.Leather
## Argentina.Agriculture                          3.1173841
## Argentina.Textile.and.Leather                  1.8329024
## Argentina.Transport.Equipment                  0.0790545
## Turkey.Agriculture                             6.9994970
## Turkey.Textile.and.Leather                    40.1671410
## Turkey.Transport.Equipment                     0.9075189
## Germany.Agriculture                            2.0595825
## Germany.Textile.and.Leather                    2.5488967
## Germany.Transport.Equipment                    1.4880228
##                               Turkey.Transport.Equipment
## Argentina.Agriculture                         0.35901126
## Argentina.Textile.and.Leather                 0.43058635
## Argentina.Transport.Equipment                 0.04024626
## Turkey.Agriculture                            1.47711579
## Turkey.Textile.and.Leather                    1.31799873
## Turkey.Transport.Equipment                    3.16041392
## Germany.Agriculture                           0.51211484
## Germany.Textile.and.Leather                   0.63316614
## Germany.Transport.Equipment                   0.56934671
##                               Germany.Agriculture
## Argentina.Agriculture                   1.2364172
## Argentina.Textile.and.Leather           0.5937041
## Argentina.Transport.Equipment           0.0231846
## Turkey.Agriculture                      2.5543089
## Turkey.Textile.and.Leather              1.1093993
## Turkey.Transport.Equipment              0.1151191
## Germany.Agriculture                    29.8763359
## Germany.Textile.and.Leather             1.4593583
## Germany.Transport.Equipment             1.7321726
##                               Germany.Textile.and.Leather
## Argentina.Agriculture                          1.30283802
## Argentina.Textile.and.Leather                  1.15375958
## Argentina.Transport.Equipment                  0.07482343
## Turkey.Agriculture                             1.52213499
## Turkey.Textile.and.Leather                     1.15207241
## Turkey.Transport.Equipment                     0.07448266
## Germany.Agriculture                            5.24719728
## Germany.Textile.and.Leather                   18.95868110
## Germany.Transport.Equipment                    1.51401054
##                               Germany.Transport.Equipment
## Argentina.Agriculture                           4.1208736
## Argentina.Textile.and.Leather                   4.7490351
## Argentina.Transport.Equipment                   0.1932621
## Turkey.Agriculture                              6.1806254
## Turkey.Textile.and.Leather                      9.5069032
## Turkey.Transport.Equipment                      0.6464733
## Germany.Agriculture                             9.6006931
## Germany.Textile.and.Leather                     8.1583150
## Germany.Transport.Equipment                    34.7438192
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{w} \hlkwb{<-} \hlkwd{wwz}\hlstd{(decompr_object)}
\end{alltt}
\end{kframe}
\end{knitrout}
